Indel Historian: fast and accurate ancestral sequence reconstruction

### 2016-07-23 doc/main.tex
revisions

\abstract{
{\bf Motivation.}
Reconstruction of indel histories and ancestral sequences is a specialized variation of multiple sequence alignment.
%The best alignment tools for ancestral reconstruction
%are not necessarily those that agree most closely with benchmark datasets based on 3D structure alignments.
In prior-published simulations,
the alignment tool ProtPal (based on a statistical phylogenetic model combining indel and substitution processes)
reconstructed indel histories more accurately than other tools,
but has proven too slow for practical use.
{\bf Results.}
Indel Historian combines an efficient reimplementation of the ProtPal algorithm with performance-improving heuristics from other alignment tools.
Supplementing the earlier simulation results on fidelity of ancestral sequence reconstruction,
evaluations on the structurally-informed datasets BAliBase and PREFAB are reported.
{\bf Availability and Implementation.}
Indel Historian is available at \url{https://github.com/ihh/indelhistorian} under the Creative Commons Attribution 3.0 US license.
{\bf Contact.}
Ian Holmes {\tt ihholmes+indelhistorian@gmail.com}.
{\bf Supplementary Information.}
None.
}

>>>>

\abstract{
{\bf Motivation.}
Reconstruction of indel histories and ancestral sequences is a specialized variation of multiple sequence alignment.
%The best alignment tools for ancestral reconstruction
%are not necessarily those that agree most closely with benchmark datasets based on 3D structure alignments.
In previously published simulations,
the alignment tool ProtPal (based on a statistical phylogenetic model combining indel and substitution processes)
reconstructed indel histories more accurately than other tools,
but has proven too slow for practical use.
{\bf Results.}
Indel Historian combines an efficient reimplementation of the ProtPal algorithm with performance-improving heuristics from other alignment tools.
Supplementing the earlier simulation results on fidelity of ancestral sequence reconstruction,
evaluations on the structurally-informed datasets BAliBase and PREFAB are reported.
{\bf Availability and Implementation.}
Indel Historian is available at \url{https://github.com/ihh/indelhistorian} under the Creative Commons Attribution 3.0 US license.
{\bf Contact.}
Ian Holmes {\tt ihholmes+indelhistorian@gmail.com}.
{\bf Supplementary Information.}
None.
}
